Project eda

### 2024-03-28 R/eda-code/eda.qmd
part 3 updated

```{r}
figure_file = here("results","figures","gender-distribution.png")
ggsave(filename = figure_file, plot=bc1) 
figure_file = here("results","figures","obesity-distribution.png")
ggsave(filename = figure_file, plot=bc3) 
figure_file = here("results","figures","obesity level by geder.png")
ggsave(filename = figure_file, plot=sbp4) 
figure_file = here("results","figures","obesity level by family history.png")
ggsave(filename = figure_file, plot=vp6) 
```

>>>>

```{r}
figure_file = here("results","figures","gender-distribution.png")
ggsave(filename = figure_file, plot=bc1) 
figure_file = here("results","figures","age-distribution.png")
ggsave(filename = figure_file, plot=hp2) 
figure_file = here("results","figures","obesity-distribution.png")
ggsave(filename = figure_file, plot=bc3) 
figure_file = here("results","figures","obesity level by geder.png")
ggsave(filename = figure_file, plot=sbp4) 
figure_file = here("results","figures","obesity level by age.png")
ggsave(filename = figure_file, plot=sbp5)
figure_file = here("results","figures","obesity level by family history.png")
ggsave(filename = figure_file, plot=vp6) 
```
